---
title: "filtering and plots"
author: "Ana Lobato"
date: "01/11/2021"
output: html_document
---

## Setting up my environment
note: setting up my R environment by loading new database "hotel_bookings.csv" and loading 2 packages :tidyverse" and "ggplot2"

```{r loading packages}
library(tidyverse)
library(ggplot2)
```

## setting up the database

```{r loding database}
hotel_bookings <- read.csv("hotel_bookings.csv")
head(hotel_bookings)
```

## Visualizations
Here we will go through a series of visualizations

### market segment
Here, we plot comparison between City Hotel and Resort Hotel

```{r}
ggplot(data = hotel_bookings)+
  geom_bar(mapping = aes(x=hotel, fill=market_segment))
```

##### facet_wrap to make more clear

```{r}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = hotel)) +
  facet_wrap(~ market_segment)
```

### filtering with piper

```{r}
online_city_hotels_v2 <- hotel_bookings %>%
  filter(hotel=="City Hotel")%>%
  filter(market_segment=="Online TA")
ggplot(data = online_city_hotels_v2)+
  geom_point(mapping = aes(x=lead_time, y=children))
```
